Vragenlijst thesis evaluatie

### 2015-05-06 doc/template/chap-2.tex
ales even updaten, related work

@@

In our assumption the strategy of both players will be non-adaptive. None of the players has information of the strategy of the opponent.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.25]{Images/FlipItDefault.jpg}
\caption{The FlipIt game where both players are playing periodically}
\label{fig:FLipItDefault}
\end{figure}
\todo{verwijzen naar de figuur \ref{fig:FLipItDefault}}

@@

 In this subsection we go through the strategies used in FlipIt and the most important results. 
 \begin{table}
 \centering
 \begin{tabular}{ l | c  }
  \textbf{Categories} & \textbf{Classes of Strategies} \\
  \hline Non-adaptive (NA) & Exponential \\
  & Periodic \\
  & Renewal \\
  & General non-adaptive \\
  \hline Adaptive (AD) & Last move (LM) \\
  & Full History (FH) \\  
\end{tabular}
 \caption{Classes of strategies in FlipIt}
 \label{table:Strategies}
 \end{table}

@@

\section{Extensions on FlipIt}

There a various possible ways to extend \flip{FlipIt}. For instance Laszka et al. extended the basic \flip{FlipIt} game to multiple resources. The incentive is that for compromising a system in a real case it needs more than just taking over one resource. An example is gaining access to a system and breaking the password. The model is called FlipThem \cite{FlipThem}. Two ways of flipping the resources are used: the AND and the OR control model. In the AND model the attacker only controls the system if he controls all the resources of the system, whereas in the OR model the attacker only needs to compromise one resource to be in control of the entire system. The difference with FlipThem and this paper is that we introduce a Graph Model in the beginning.\\
Another extension on FlipIt is done by Pham\cite{GameTheorApprCostBenefitAnalyses} [\todo{citatie needed voor Are We Compromised?}]. Beside the action Flip their is another action Test. The basic idea is to test with an extra action if the resource has been compromised or not. This action involves also an extra cost. This model is useful if somebody wants to know for example if his password has been compromised or wants to assess the periodic security of a system.  In \cite{MitigationCovert} \cite{MitigationNonTargeted} Laszka et al. they also consider non targeted attacks by non-strategic players and \todo{verder aanvullen}. \\

>>>>

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.8]{Images/DefFlipit}
\caption{A representation of a FlipIt game where both players are playing periodically and discrete. Every move or "flip" is indicated by a blue or orange circle. The blue and orange rectangles represent the amount of time one of the players is in control of the resource.}
\label{fig:FLipItDefault}
\end{figure}
\todo{verwijzen naar de figuur \ref{fig:FLipItDefault}}

@@

In our analyses of the FlipIt game with a virus propagation in section [], we assume the strategy of both players to be non-adaptive. None of the players has information of the strategy of the opponent. The defender will never know when the attacker will attack the network with a virus. Conversely, the attacker does not know how often the defender defends his network.

@@

 In this subsection we elaborate about the strategy of FlipIt . For the other strategies of FlipIt we refer the reader to [the paper of FlipIt]
 \begin{table}
 \centering
 \begin{tabular}{ l | c  }
  \textbf{Categories} & \textbf{Classes of Strategies} \\
  \hline Non-adaptive (NA) & Exponential \\
  & Periodic \\
  & Renewal \\
  & General non-adaptive \\
  \hline Adaptive (AD) & Last move (LM) \\
  & Full History (FH) \\  
\end{tabular}
 \caption{Classes of strategies in FlipIt}
 \label{table:Strategies}
 \end{table}

@@

### 2015-05-06 doc/template/chap-3.tex
alles committen
ales even updaten, related work

%\chapter{Intoduction to GameTheory}
%\label{cha:1}
\documentclass[10pt]{article}
\begin{document}

\section{Gametheory}

Game theory is the study between self interested agents and the actions they perform. self interested agents means not that they want to harm each other or that they only care about themselves. Agent has a description of the world he likes. A utility function is a mapping of the world that the agent likes to real numbers.

\section{Literatuurstudie}

@@

@@

\end{document}

>>>>

\chapter{Related work}
\label{cha:1}

\section{Related work}

@@

\section{Extensions on FlipIt}

In this section we discuss the extentions that can be made on the FlipIt game.

There a various possible ways to extend \flip{FlipIt}. 
Laszka et al. made a lot of additions and extensions on the original game of FlipIt. For instance Laszka et al. extended the basic \flip{FlipIt} game to multiple resources. The incentive is that for compromising a system in a real case it needs more than just taking over just one resource. An example is that one resource can be gaining access to a system and breaking the password of the system is another resource. The model is called FlipThem \cite{FlipThem}. They use two ways to flip the multiple resources: the AND and the OR control model. In the AND model the attacker only controls the system if he controls all the resources of the system, whereas in the OR model the attacker only needs to compromise one resource to be in control of the entire system. %The difference with FlipThem and this paper is that we introduce a Graph Model in the beginning.\\
Another addition of Laszka et al. to the game of FlipIt is extending the game to also consider non-targeted attacks by non-strategic players. In this game the defender tries to maintain control over the resource that is subjected to both targeted and non-targeted attacks.

A last important addition from Laszka et al. to the game of FlipIt is   The moves made by the attacker are still covert but the moves made by the defender are known to the attacker. This means that the attacker can base his attacks on the defender's moves. Both the targeted and non-targeted attacks don't succeed immidiatly. For the targeted attack the time till it succeeds is given by an exponential distributed random variable with a known rate. The non-targeted attacks are modelled as a single attacker and the time till it succeeds is given by a Poisson process.\todo{misschien meer uitleggen}. The conclusion of this paper is that the optimal strategy for the defender is moving periodically.

on FlipIt is done by Pham\cite{GameTheorApprCostBenefitAnalyses} [\todo{citatie needed voor Are We Compromised?}]. Beside the action Flip their is another action Test. The basic idea is to test with an extra action if the resource has been compromised or not. This action involves also an extra cost. This model is useful if somebody wants to know for example if his or her password has been compromised or wants to assess the periodic security of a system.  In \cite{MitigationCovert} \cite{MitigationNonTargeted} Laszka et al. they also consider non targeted attacks by non-strategic players and \todo{verder aanvullen}. \\

@@
